---
title: "REU2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
setwd("C:/Users/kzilla/Documents/REU2020/")
```
```{r}
#install.packages("tidyverse")
#install.packages("patchwork")
#install.packages("RColorBrewer")
```
```{r}
library(tidyverse)
library(patchwork)
library(RColorBrewer)
library(ggplot2)
```

#CM = chromosomes
#JAA = Scaffolds (not sure where they are)
#endpoints can be used as length of scaffold, coverage percentage,
#use meandepth instead of coverage
```{r}
netAur_M.tb <- read_tsv("netAur_male.sort.coverage.out")
netAur_M.tb
netAur_Fem.tb <- read_tsv("netAur_female.sort.coverage.out")
netAur_Fem.tb
#netAur_F1.tb <- read_tsv("netAur_female_L001_001.sort.coverage.out")
#netAur_F1.tb
#netAur_F4.tb <- read_tsv("netAur_female_L004_001.sort.coverage.out")
```
#Changing 1st colomn name from rname to chromosome
```{r}
NA_male <- netAur_M.tb %>% rename(chromosome = "#rname")
NA_male
NA_female <- netAur_Fem.tb %>% rename(chromosome = "#rname")
NA_female
#NA_Fem1 <- netAur_F1.tb %>% rename(chromosome = "#rname")
#NA_Fem1
#NA_Fem4 <- netAur_F4.tb %>% rename(chromosome = "#rname")
#NA_Fem4
```

```{r}
NA_male.selected <- NA_male %>% select(chromosome,startpos,endpos,meandepth) %>% filter(endpos > 1e6) %>% mutate(meandp = mean(meandepth),normdp = meandepth/meandp,sex = "M") %>%  arrange(desc(normdp))
NA_male.selected

NA_fem.selected <- NA_female %>% select(chromosome,startpos,endpos,meandepth) %>% filter(endpos > 100000) %>% mutate(meandp = mean(meandepth),normdp = meandepth/meandp,sex = "F") %>%  arrange(desc(normdp))
NA_fem.selected
#NA_Fem1.selected <- NA_Fem1 %>% select(chromosome,startpos,endpos,meandepth) %>% filter(endpos > 100000) %>% mutate(meandp = mean(meandepth),normdp = meandepth/meandp,sex = "F1") %>% arrange(normdp)
#NA_Fem1.selected
#NA_Fem4.selected <- NA_Fem4 %>% select(chromosome,startpos,endpos,meandepth) %>% filter(endpos > 100000) %>% mutate(meandp = mean(meandepth),normdp = meandepth/meandp,sex = "F4") %>% arrange(normdp)
#NA_Fem4.selected
```
#StiNai table with male and fem combined
#filter autosomes in Fem aswell, filter
```{r}
NA_male.selected.filter <- NA_male.selected %>% filter(normdp > 0.8,normdp < 1.2)
NA_male.selected.filter

NA_fem.selected.filter <- NA_fem.selected %>% filter(normdp < 0.6)
NA_fem.selected.filter

#NA_Fem1.selected.filter <- NA_Fem1.selected %>% filter(normdp < 0.6)
#NA_Fem1.selected.filter
#NA_Fem4.selected.filter <- NA_Fem4.selected %>% filter(normdp < 0.6)
#NA_Fem4.selected.filter

netAur.filter.all <- combine(NA_male.selected.filter, NA_fem.selected.filter) %>% arrange(chromosome)
netAur.filter.all
```
#Create Bed file with scaffold start-1, and end
#In the male sample, select 3 autosomes between 1 million and 10 million
```{r}
NA_Male.bed <- NA_male.selected.filter %>% mutate(start=startpos-1) %>% select(chromosome,start,endpos) %>% filter(endpos>1000000,endpos<10000000) %>% filter(chromosome == "CM021788.1"|chromosome == "CM021791.1" |chromosome == "CM021787.1") 
NA_Male.bed

NA_Fem.bed <- NA_fem.selected.filter %>% mutate(start=startpos-1) %>% select(chromosome,start,endpos)
NA_Fem.bed

#NA_Fem1.bed <- NA_Fem1.selected.filter %>% mutate(start=startpos-1) %>% select(chromosome,start,endpos)
#NA_Fem1.bed
#NA_Fem4.bed <- NA_Fem4.selected.filter %>% mutate(start=startpos-1) %>% select(chromosome,start,endpos)
#NA_Fem4.bed
```
#Export/write the bed files
```{r}
write_tsv(NA_Male.bed,"NA_Male.bed",col_names = F) 
write_tsv(NA_Fem.bed,"NA_Fem.bed",col_names = F)
#write_tsv(NA_Fem1.bed,"NA_Fem1.bed",col_names = F)
#write_tsv(NA_Fem4.bed,"NA_Fem4.bed",col_names = F)
```
#filter male sex chromosomes and female autosomes and create bed files to run samtools depth
```{r}
NA_male.chromosomes <- NA_male %>% filter(chromosome == 'CM021788.1'|chromosome == 'CM021787.1'|chromosome == 'CM021791.1') %>% mutate(start=startpos-1) %>% select(chromosome,start,endpos)
NA_male.chromosomes
write_tsv(NA_male.chromosomes,'NA_male.chromosomes.bed',col_names = F)
NA_female.autosomes <- NA_female %>% filter(chromosome == 'MU016689.1'|chromosome == 'MU016692.1'|chromosome == 'MU016690.1') %>%  mutate(start=startpos-1) %>% select(chromosome,start,endpos)
NA_female.autosomes
write_tsv(NA_female.autosomes,'NA_female.autosomes.bed',col_names = F)
```
#Load in autosome data from samtool depth on Male sample
```{r}
autosome.male.lst <- read_delim("NA_Male.depth.txt",delim = "\t",col_names = F)
autosome.male.lst
autosome.female.lst <- read_delim("NA_female.autosomes.depth.txt",delim = "\t",col_names = F)
autosome.female.lst
#male_autosomes <- read_delim("NA_Male.depth.txt",delim = "\t",col_names = F) %>% rename(scaffold = X1, pos = X2, cov = X3) %>% mutate(chr = 'auto') %>% select(chr,cov)
#male_autosomes
```
#Load in possible sex chromosome data from samtool depth on female
```{r}
fem1_sexChr <- read_delim("NA_Fem1.depth.txt",delim = "\t",col_names = F) %>% rename(scaffold = X1, pos = X2, cov = X3) %>% mutate(chr = 'sex') %>% select(chr, cov)
fem1_sexChr

fem4_sexChr <- read_delim("NA_Fem4.depth.txt",delim = "\t",col_names = F) %>% rename(scaffold = X1, pos = X2, cov = X3) %>% mutate(chr = 'sex') %>% select(chr, cov)
fem4_sexChr

fem_sexChr <- read_delim("NA_fem.depth.txt",delim = "\t",col_names = F) %>% rename(scaffold = X1, pos = X2, cov = X3) %>% mutate(chr = 'sex') %>% select(chr, cov)
fem_sexChr

femcombined_temp <- combine(fem1_sexChr, fem4_sexChr)
femcombined_temp
```
```{r}
#as_fem1 <- bind_rows(male_autosomes,fem1_sexChr) %>% filter(cov < 100)
#as_fem4 <- bind_rows(male_autosomes,fem4_sexChr) %>% filter(cov < 100)
as_fem <- bind_rows(male_autosomes,fem_sexChr) %>% filter(cov < 100)
as_femcomb <- bind_rows(male_autosomes,femcombined_temp) %>% filter(cov < 100)
```
```{r}
ggplot(as_fem, aes(cov, color = chr,y = ..density..)) + geom_freqpoly(alpha = 0.5, position = 'identity', binwidth = 3)

```
```{r}
ggplot(as_femcomb, aes(cov, color = chr,y = ..density..)) + geom_freqpoly(alpha = 0.5, position = 'identity', binwidth = 3)
```
#plot one autosome to all sex chromosomes  
```{r}
chromosome_CM021787.1_M <- autosome.male.lst %>% filter(X1 == 'CM021787.1') %>% rename(scaffold = X1, pos = X2, cov = X3) %>%  mutate(chr = 'auto') %>% select(chr, cov)
chromosome_CM021787.1_M
#chromosome_CM021787.1_F <- NA_fem.selected %>% filter(chromosome == 'CM021787.1') %>% mutate(sex = 'F')
#chromosome_CM021787.1_F
CM021787.1.merge <- combine(fem_sexChr,chromosome_CM021787.1_M) %>% filter(cov < 100)
ggplot(CM021787.1.merge, aes(cov, color = chr,y = ..density..)) + geom_freqpoly(alpha = 0.5, position = 'identity', binwidth = 3)
chromosome_CM021788.1_M <- autosome.male.lst %>% filter(X1 == 'CM021788.1') %>% rename(scaffold = X1, pos = X2, cov = X3) %>%  mutate(chr = 'auto') %>% select(chr, cov)
chromosome_CM021788.1_M
#chromosome_CM021788.1_F <- NA_fem.selected %>% filter(chromosome == 'CM021788.1') %>% mutate(sex = 'F')
#chromosome_CM021788.1_F
CM021788.1.merge <- combine(fem_sexChr,chromosome_CM021788.1_M) %>% filter(cov < 100)
ggplot(CM021788.1.merge, aes(cov, color = chr,y = ..density..)) + geom_freqpoly(alpha = 0.5, position = 'identity', binwidth = 3)
chromosome_CM021791.1_M <- autosome.male.lst %>% filter(X1 == 'CM021791.1') %>% rename(scaffold = X1, pos = X2, cov = X3) %>%  mutate(chr = 'auto') %>% select(chr, cov)
chromosome_CM021791.1_M
#chromosome_CM021791.1_F <- NA_fem.selected %>% filter(chromosome == 'CM021791.1') %>% mutate(sex = 'F')
#chromosome_CM021791.1_F
CM021791.1.merge <- combine(fem_sexChr,chromosome_CM021791.1_M) %>% filter(cov < 100)
ggplot(CM021791.1.merge, aes(cov, color = chr,y = ..density..)) + geom_freqpoly(alpha = 0.5, position = 'identity', binwidth = 3)
```
#load in list of scaffolds for female and male
```{r}
#autosome.male.lst <- read_delim("NA_Male.depth.txt",delim = "\t",col_names = F) %>% rename(scaffold = X1, pos = X2, cov = X3) %>% mutate(chr = 'auto')
#autosome.male.lst
#fem_sexChr <- read_delim("NA_fem.depth.txt",delim = "\t",col_names = F) %>% rename(scaffold = X1, pos = X2, cov = X3) %>% mutate(chr = 'sex') 
#fem_sexChr
```
#Load in possible sex chromosome data from samtool depth on female and male sample
```{r}
fem_sexChr <- read_delim("NA_fem.depth.txt",delim = "\t",col_names = F) %>% rename(scaffold = X1, pos = X2, cov = X3) %>% mutate(sex = 'F') %>% select(sex, cov)
fem_sexChr

male_sexChr <- read_delim("NA_male.chromosomes.depth.txt",delim = "\t",col_names = F) %>% rename(scaffold = X1, pos = X2, cov = X3) %>% mutate(sex = 'M') %>% select(sex, cov)
male_sexChr
```
#plot each scaffold and confirm identity
```{r}
fem_MU016689.1 <- NA_female %>% filter(chromosome == 'MU016689.1') %>% select(chromosome,coverage) %>% mutate(sex = 'F')
male_MU016689.1 <- NA_male %>% filter(chromosome == 'MU016689.1') %>% select(chromosome,coverage) %>% mutate(sex = 'M')
MU016689.1 <- combine(fem_MU016689.1,male_MU016689.1) %>% mutate(location = 'W chromosome')
MU016689.1
ggplot(MU016689.1, aes(coverage, color = sex,y = ..density..)) + geom_freqpoly(alpha = 0.5, position = 'identity', binwidth = 3)
ggplot(MU016689.1, aes(coverage, fill = sex)) + geom_histogram(alpha = 0.5, position = 'identity', binwidth = 3)
ggplot(MU016689.1, aes(coverage, fill = sex)) + geom_bar(alpha = 0.5, position = 'identity', binwidth = 3)
fem_MU016692.1 <- NA_female %>% filter(chromosome == 'MU016692.1') %>% select(chromosome,coverage) %>% mutate(sex = 'F')
male_MU016692.1 <- NA_male %>% filter(chromosome == 'MU016692.1') %>% select(chromosome,coverage) %>% mutate(sex = 'M')
MU016692.1 <- combine(fem_MU016692.1,male_MU016692.1) %>% mutate(location = 'W chromosome')
MU016692.1

fem_MU016690.1 <- NA_female %>% filter(chromosome == 'MU016690.1') %>% select(chromosome,coverage) %>% mutate(sex = 'F')
male_MU016690.1 <- NA_male %>% filter(chromosome == 'MU016690.1') %>% select(chromosome,coverage) %>% mutate(sex = 'M')
MU016690.1 <- combine(fem_MU016690.1,male_MU016690.1) %>% mutate(location = 'W chromosome')
MU016690.1

male_CM021788.1 <- NA_male %>% filter(chromosome == 'CM021788.1') %>% select(chromosome,coverage) %>% mutate(sex = 'M')
fem_CM021788.1 <- NA_female %>% filter(chromosome == 'CM021788.1') %>% select(chromosome,coverage) %>% mutate(sex = 'F')
CM021788.1 <- combine(male_CM021788.1,fem_CM021788.1) %>% mutate(location = 'autosome')
CM021788.1

male_CM021787.1 <- NA_male %>% filter(chromosome == 'CM021787.1') %>% select(chromosome,coverage) %>% mutate(sex = 'M')
fem_CM021787.1 <- NA_female %>% filter(chromosome == 'CM021787.1') %>% select(chromosome,coverage) %>% mutate(sex = 'F')
CM021787.1 <- combine(male_CM021787.1,fem_CM021787.1) %>% mutate(location = 'autosome')
CM021787.1

male_CM021791.1 <- NA_male %>% filter(chromosome == 'CM021791.1') %>% select(chromosome,coverage) %>% mutate(sex = 'M')
fem_CM021791.1 <- NA_female %>% filter(chromosome == 'CM021791.1') %>% select(chromosome,coverage) %>% mutate(sex = 'F')
CM021791.1 <- combine(male_CM021791.1,fem_CM021791.1) %>% mutate(location = 'autosome')
CM021791.1
```
#combine all possible scaffold identities
```{r}
netAur.chromosome.locations <- combine(MU016689.1, MU016692.1, MU016690.1, CM021788.1, CM021787.1, CM021791.1)
netAur.chromosome.locations
```
#plot male autosomes vs female autosomes
```{r}
autosome.M <- autosome.male.lst %>% rename(scaffold = X1, pos = X2, cov = X3) %>%  mutate(sex = 'M') %>% select(sex, cov)
autosome.M
autosome.F <- autosome.female.lst %>% rename(scaffold = X1, pos = X2, cov = X3) %>%  mutate(sex = 'F') %>% select(sex, cov)
autosome.merge <- combine(autosome.F,autosome.M) %>% filter(cov < 100)
ggplot(autosome.merge, aes(cov, color = sex,y = ..density..)) + geom_freqpoly(alpha = 0.5, position = 'identity', binwidth = 3)
ggplot(autosome.merge, aes(cov, fill = sex)) + geom_histogram(alpha = 0.5, position = 'identity', binwidth = 3)

```
#plot male and female sex chromosomes
```{r}
sexChr.merge <- combine(fem_sexChr,male_sexChr) %>% filter(cov < 100)
ggplot(sexChr.merge, aes(cov, color = sex,y = ..density..)) + geom_freqpoly(alpha = 0.5, position = 'identity', binwidth = 3)
ggplot(sexChr.merge, aes(cov, fill = sex)) + geom_histogram(alpha = 0.5, position = 'identity', binwidth = 3)
```
#heatmap 
```{r}
fem_sexChr.filt <- fem_sexChr %>% filter(cov <250)
ggplot(fem_sexChr.filt, aes(cov, fill = sex)) + geom_histogram(alpha = 0.5, position = 'identity', binwidth = 3)
```
#calculate mean and median
```{r}
mean(autosome.M$cov) 
median(autosome.M$cov)
mean(autosome.F$cov)
median(autosome.F$cov)
mean(fem_sexChr$cov)
median(fem_sexChr$cov)
mean(male_sexChr$cov)
median(male_sexChr$cov)
```
#Make various plots
```{r}
ggplot(NA_male, aes(x=coverage, y=log10(meandepth))) + geom_point()
ggplot(NA_male, aes(x=coverage, y=meanmapq)) + geom_point()
ggplot(NA_male, aes(x=meanmapq, y=log10(meandepth))) + geom_point()
ggplot(NA_male, aes(x=coverage, y=log10(endpos))) + geom_point()
ggplot(NA_male, aes(x=meanmapq, y=log10(endpos))) + geom_point()
```
```{r}
ggplot(NA_female, aes(x=coverage, y=log10(meandepth))) + geom_point()
ggplot(NA_female, aes(x=coverage, y=meanmapq)) + geom_point()
ggplot(NA_female, aes(x=meanmapq, y=log10(meandepth))) + geom_point()
ggplot(NA_female, aes(x=coverage, y=log10(endpos))) + geom_point()
ggplot(NA_female, aes(x=meanmapq, y=log10(endpos))) + geom_point()
```
#normalize meandepth
```{r}
NA_male %>% filter(endpos > 1e6) %>% mutate(weighted_depth = meandepth * endpos) %>% summarize(wt_norm_dp = sum(weighted_depth)/sum(endpos))
NA_male_norm <- NA_male %>% mutate(normdp = meandepth/37.05507)
NA_male_norm
NA_female %>% filter(endpos > 1e6, meandepth > 30) %>% mutate(weighted_depth = meandepth * endpos) %>% summarize(wt_norm_dp = sum(weighted_depth)/sum(endpos))
NA_female_norm <- NA_female %>% mutate(normdp = meandepth/40.69054)
NA_female_norm
```
#plot normdp vs meanmapq and endpos to determine good cutoffs
```{r}
ggplot(NA_female_norm, aes(x=meanmapq, y=log10(normdp))) + geom_point()
ggplot(NA_female_norm, aes(x=log10(normdp), y=log10(endpos))) + geom_point()
ggplot(NA_male_norm, aes(x=meanmapq, y=log10(normdp))) + geom_point()
ggplot(NA_male_norm, aes(x=log10(normdp), y=log10(endpos))) + geom_point()
```
#plot normdp in males vs females
```{r}
NA_both <- full_join(NA_male_norm, NA_female_norm, by=c('chromosome' = 'chromosome', 'endpos' = 'endpos'), suffix=c('.male', '.female'))
NA_both
NA_both %>% filter(endpos > 1e5, meanmapq.female > 20, coverage.female > 50) %>% ggplot(aes(x=normdp.male, y=normdp.female)) + geom_point()
NA_both %>% mutate(rel.dp = normdp.male / normdp.female) %>% filter(rel.dp < 3) %>% ggplot(aes(x=rel.dp)) + geom_histogram(bins = 60)
# filter(endpos > 1e4, meanmapq.female > 20, coverage.female > 50) %>%
```
#z = normdp.fem 0.6-1 normd.male .75-1
autosome = normdp.fem 1.2-1.8 normdp.male 0.6-1
W = normdp. fem 0-1 norm.dp.male0*0.1
W maybe .4-.8 femmale .1-.4
```{r}
NA_W <- NA_both %>% filter(normdp.female > 0,normdp.female < 1,normdp.male > 0, normdp.male < 0.1) %>% mutate(chr = 'W')
NA_W
NA_Z <- NA_both %>% filter(normdp.female > 0.6,normdp.female < 1,normdp.male > 0.75, normdp.male < 1) %>% mutate(chr = 'Z')
NA_Z
NA_Auto <- NA_both %>% filter(normdp.female > 1.2,normdp.female < 1.8,normdp.male > 0.6, normdp.male < 1) %>% mutate(chr = 'Autosome')
NA_Auto
NA_possible_W <- NA_both %>% filter(normdp.female > 0.4,normdp.female < .8,normdp.male > 0.1, normdp.male < 0.4) %>% mutate(chr = 'Possible W')
NA_possible_W
NA_both_filtered <- rbind(NA_Z,NA_W,NA_possible_W,NA_Auto) %>% mutate(rel.dp = normdp.male / normdp.female)
NA_both_filtered
```

#add chromsome assignments to NA_both
```{r}
ggplot(NA_both_filtered, aes(x=rel.dp, col=chr))+ geom_histogram(bins=50)
ggplot(NA_both_filtered, aes(x=rel.dp,y=normdp.female, col=chr))+ geom_point()
ggplot(NA_both_filtered, aes(x=normdp.male,y=normdp.female, col=chr))+ geom_point()

```

