---
title: "REU2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
#setwd("C:/Users/kzilla/Documents/REU2020/")
```
```{r}
#install.packages("tidyverse")
#install.packages("patchwork")
#install.packages("RColorBrewer")
```
```{r}
library(tidyverse)
library(patchwork)
library(RColorBrewer)
library(ggplot2)
```

#CM = chromosomes
#JAA = Scaffolds (not sure where they are)
#endpoints can be used as length of scaffold, coverage percentage,
#use meandepth instead of coverage
```{r}
oxyJam_M.tb <- read_tsv("oxyJam_male.sort.coverage.out")
oxyJam_M.tb
oxyJam_Fem.tb <- read_tsv("oxyJam_female.sort.coverage.out")
oxyJam_Fem.tb
#oxyJam_F1.tb <- read_tsv("oxyJam_female_L001_001.sort.coverage.out")
#oxyJam_F1.tb
#oxyJam_F4.tb <- read_tsv("oxyJam_female_L004_001.sort.coverage.out")
```
#Changing 1st colomn name from rname to chromosome
```{r}
OJ_male <- oxyJam_M.tb %>% rename(chromosome = "#rname")
OJ_male
OJ_female <- oxyJam_Fem.tb %>% rename(chromosome = "#rname")
OJ_female
#OJ_Fem1 <- oxyJam_F1.tb %>% rename(chromosome = "#rname")
#OJ_Fem1
#OJ_Fem4 <- oxyJam_F4.tb %>% rename(chromosome = "#rname")
#OJ_Fem4
```

```{r}
OJ_male.selected <- OJ_male %>% select(chromosome,startpos,endpos,meandepth) %>% filter(endpos > 1e6) %>% mutate(meandp = mean(meandepth),normdp = meandepth/meandp,sex = "M") %>%  arrange(desc(normdp))
OJ_male.selected

OJ_fem.selected <- OJ_female %>% select(chromosome,startpos,endpos,meandepth) %>% filter(endpos > 100000) %>% mutate(meandp = mean(meandepth),normdp = meandepth/meandp,sex = "F") %>%  arrange(desc(normdp))
OJ_fem.selected

#OJ_Fem1.selected <- OJ_Fem1 %>% select(chromosome,startpos,endpos,meandepth) %>% filter(endpos > 100000) %>% mutate(meandp = mean(meandepth),normdp = meandepth/meandp,sex = "F1") %>% arrange(normdp)
#OJ_Fem1.selected
#OJ_Fem4.selected <- OJ_Fem4 %>% select(chromosome,startpos,endpos,meandepth) %>% filter(endpos > 100000) %>% mutate(meandp = mean(meandepth),normdp = meandepth/meandp,sex = "F4") %>% arrange(normdp)
#OJ_Fem4.selected
```
#StiOJi table with male and fem combined
```{r}
OJ_male.selected.filter <- OJ_male.selected %>% filter(normdp > 0.8,normdp < 1.2)
OJ_male.selected.filter

OJ_fem.selected.filter <- OJ_fem.selected %>% filter(normdp < 0.6)
OJ_fem.selected.filter

#OJ_Fem1.selected.filter <- OJ_Fem1.selected %>% filter(normdp < 0.6)
#OJ_Fem1.selected.filter

#OJ_Fem4.selected.filter <- OJ_Fem4.selected %>% filter(normdp < 0.6)
#OJ_Fem4.selected.filter

#oxyJam.filter.all <- rbind(OJ_male.selected.filter, OJ_fem.selected.filter) %>% arrange(chromosome)
#oxyJam.filter.all
```

#Create Bed file with scaffold start-1, and end
#In the male sample, select 3 autosomes between 1 million and 10 million
```{r}
OJ_Male.bed <- OJ_male.selected.filter %>% mutate(start=startpos-1) %>% select(chromosome,start,endpos) %>% filter(endpos>1000000,endpos<10000000) %>% filter(chromosome == "CM021822.1"|chromosome == "CM021821.1" |chromosome == "CM021825.1")
OJ_Male.bed

OJ_Fem.bed <- OJ_fem.selected.filter %>% mutate(start=startpos-1) %>% select(chromosome,start,endpos)
OJ_Fem.bed
#OJ_Fem1.bed <- OJ_Fem1.selected.filter %>% mutate(start=startpos-1) %>% select(chromosome,start,endpos)
#OJ_Fem1.bed

#OJ_Fem4.bed <- OJ_Fem4.selected.filter %>% mutate(start=startpos-1) %>% select(chromosome,start,endpos)
#OJ_Fem4.bed
```
#Export/write the bed files
```{r}
write_tsv(OJ_Male.bed,"OJ_Male.bed",col_names = F)
write_tsv(OJ_Fem.bed,"OJ_Fem.bed",col_names = F)
#write_tsv(OJ_Fem1.bed,"OJ_Fem1.bed",col_names = F)
#write_tsv(OJ_Fem4.bed,"OJ_Fem4.bed",col_names = F)
```
#filter male sex chromosomes and female autosomes and create bed files to run samtools depth
```{r}
OJ_male.chromosomes <- OJ_male %>% filter(chromosome == 'CM021822.1'|chromosome == 'CM021821.1'|chromosome == 'CM021825.1') %>% mutate(start=startpos-1) %>% select(chromosome,start,endpos)
OJ_male.chromosomes
#CM021822.1 CM021821.1 CM021825.1
write_tsv(OJ_male.chromosomes,'OJ_male.chromosomes.bed',col_names = F)
OJ_female.autosomes <- OJ_female %>% filter(chromosome == 'MU018450.1'|chromosome == 'MU018386.1'|chromosome == 'MU017945.1'|chromosome == 'MU018675.1'|chromosome == 'MU017919.1'|chromosome == 'MU017967.1'|chromosome == 'MU018416.1'|chromosome == 'MU018370.1'|chromosome == 'MU018302.1'|chromosome == 'MU018677.1'|chromosome == 'MU017909.1'|chromosome == 'MU018361.1'|chromosome == 'MU017883.1'|chromosome == 'MU018405.1') %>%  mutate(start=startpos-1) %>% select(chromosome,start,endpos)
OJ_female.autosomes
write_tsv(OJ_female.autosomes,'OJ_female.autosomes.bed',col_names = F)
#MU018450.1	MU018386.1 MU017945.1	MU018675.1 MU017919.1 MU017967.1	MU018416.1 MU018370.1 MU018302.1 MU018677.1 MU017909.1 MU018361.1 MU017883.1 MU018405.1
```
#Load in autosome data from samtool depth on Male and female sample
```{r}
autosome.male.lst <- read_delim("OJ_Male.depth.txt",delim = "\t",col_names = F)
autosome.male.lst
autosome.female.lst <- read_delim("OJ_female.autosomes.depth.txt",delim = "\t",col_names = F)
autosome.female.lst
#male_autosomes <- read_delim("OJ_Male.depth.txt",delim = "\t",col_names = F) %>% rename(scaffold = X1, pos = X2, cov = X3) %>% mutate(chr = 'auto') %>% select(chr,cov)
#male_autosomes
```
#Load in possible sex chromosome data from samtool depth on female and male sample
```{r}
#fem1_sexChr <- read_delim("OJ_Fem1.depth.txt",delim = "\t",col_names = F) %>% rename(scaffold = X1, pos = X2, cov = X3) %>% mutate(chr = 'sex') %>% select(chr, cov)
#fem1_sexChr

#fem4_sexChr <- read_delim("OJ_Fem4.depth.txt",delim = "\t",col_names = F) %>% rename(scaffold = X1, pos = X2, cov = X3) %>% mutate(chr = 'sex') %>% select(chr, cov)
#fem4_sexChr

fem_sexChr <- read_delim("OJ_fem.depth.txt",delim = "\t",col_names = F) %>% rename(scaffold = X1, pos = X2, cov = X3) %>% mutate(sex = 'F') %>% mutate(chr = 'Sex Chromosomes') %>% select(chr, cov)
fem_sexChr

male_sexChr <- read_delim("OJ_male.chromosomes.depth.txt",delim = "\t",col_names = F) %>% rename(scaffold = X1, pos = X2, cov = X3) %>% mutate(chr = 'Sex Chromosomes') %>% select(chr, cov)
male_sexChr
#femcombined_temp <- rbind(fem1_sexChr, fem4_sexChr)
#femcombined_temp

```
```{r}
#as_fem1 <- bind_rows(male_autosomes,fem1_sexChr) %>% filter(cov < 100)
#as_fem4 <- bind_rows(male_autosomes,fem4_sexChr) %>% filter(cov < 100)
#ggplot(as_fem1, aes(cov, fill =chr)) + geom_histogram(alpha = 0.5, position = 'identity', binwidth = 3)
#ggplot(as_fem4, aes(cov, fill =chr)) + geom_histogram(alpha = 0.5, position = 'identity', binwidth = 3)
```
#plot one autosome to all sex chromosomes  
```{r}
chromosome_CM021822.1_M <- autosome.male.lst %>% filter(X1 == 'CM021822.1') %>% rename(scaffold = X1, pos = X2, cov = X3) %>%  mutate(chr = 'auto') %>% select(chr, cov)
chromosome_CM021822.1_M
CM021822.1.merge <- rbind(fem_sexChr,chromosome_CM021822.1_M) %>% filter(cov < 100) 
ggplot(CM021822.1.merge, aes(cov, color = chr,y = ..density..)) + geom_freqpoly(alpha = 0.5, position = 'identity', binwidth = 3)

chromosome_CM021821.1_M <- autosome.male.lst %>% filter(X1 == 'CM021821.1') %>% rename(scaffold = X1, pos = X2, cov = X3) %>%  mutate(chr = 'auto') %>% select(chr, cov)
chromosome_CM021821.1_M
CM021821.1.merge <- rbind(fem_sexChr,chromosome_CM021821.1_M) %>% filter(cov < 100)
ggplot(CM021821.1.merge, aes(cov, color = chr,y = ..density..)) + geom_freqpoly(alpha = 0.5, position = 'identity', binwidth = 3)

chromosome_CM021825.1_M <- autosome.male.lst %>% filter(X1 == 'CM021825.1') %>% rename(scaffold = X1, pos = X2, cov = X3) %>%  mutate(chr = 'auto') %>% select(chr, cov)
chromosome_CM021825.1_M
CM021825.1.merge <- rbind(fem_sexChr,chromosome_CM021825.1_M) %>% filter(cov < 100)
ggplot(CM021825.1.merge, aes(cov, color = chr,y = ..density..)) + geom_freqpoly(alpha = 0.5, position = 'identity', binwidth = 3)
```
#plot each scaffold and confirm identity of autosomes
```{r}
male_CM021822.1 <- OJ_male %>% filter(chromosome == 'CM021822.1') %>% select(chromosome,coverage) %>% mutate(sex = 'M')
fem_CM021822.1 <- OJ_female %>% filter(chromosome == 'CM021822.1') %>% select(chromosome,coverage) %>% mutate(sex = 'F')
CM021822.1 <- rbind(male_CM021822.1,fem_CM021822.1) %>% mutate(location = 'autosome')
CM021822.1

male_CM021821.1 <- OJ_male %>% filter(chromosome == 'CM021821.1') %>% select(chromosome,coverage) %>% mutate(sex = 'M')
fem_CM021821.1 <- OJ_female %>% filter(chromosome == 'CM021821.1') %>% select(chromosome,coverage) %>% mutate(sex = 'F')
CM021821.1 <- rbind(male_CM021821.1,fem_CM021821.1) %>% mutate(location = 'autosome')
CM021821.1 

male_CM021825.1 <- OJ_male %>% filter(chromosome == 'CM021825.1') %>% select(chromosome,coverage) %>% mutate(sex = 'M')
fem_CM021825.1 <- OJ_female %>% filter(chromosome == 'CM021825.1') %>% select(chromosome,coverage) %>% mutate(sex = 'F')
CM021825.1 <- rbind(male_CM021825.1,fem_CM021825.1) %>% mutate(location = 'autosome')
CM021825.1 

#CM021822.1 CM021821.1 CM021825.1
```
#plot each scaffold and confirm identity of 'W' chromosomes
```{r}
fem_MU018450.1 <- OJ_female %>% filter(chromosome == 'MU018450.1') %>% select(chromosome,coverage) %>% mutate(sex = 'F')
male_MU018450.1 <- OJ_male %>% filter(chromosome == 'MU018450.1') %>% select(chromosome,coverage) %>% mutate(sex = 'M')
MU018450.1 <- rbind(fem_MU018450.1,male_MU018450.1) %>% mutate(location = 'W chromosome')
MU018450.1

fem_MU018386.1 <- OJ_female %>% filter(chromosome == 'MU018386.1') %>% select(chromosome,coverage) %>% mutate(sex = 'F')
male_MU018386.1 <- OJ_male %>% filter(chromosome == 'MU018386.1') %>% select(chromosome,coverage) %>% mutate(sex = 'M')
MU018386.1 <- rbind(fem_MU018386.1,male_MU018386.1) %>% mutate(location = 'W chromosome')
MU018386.1

fem_MU017945.1 <- OJ_female %>% filter(chromosome == 'MU017945.1') %>% select(chromosome,coverage) %>% mutate(sex = 'F')
male_MU017945.1 <- OJ_male %>% filter(chromosome == 'MU017945.1') %>% select(chromosome,coverage) %>% mutate(sex = 'M')
MU017945.1 <- rbind(fem_MU017945.1,male_MU017945.1) %>% mutate(location = 'W chromosome')
MU017945.1

fem_MU018675.1 <- OJ_female %>% filter(chromosome == 'MU018675.1') %>% select(chromosome,coverage) %>% mutate(sex = 'F')
male_MU018675.1 <- OJ_male %>% filter(chromosome == 'MU018675.1') %>% select(chromosome,coverage) %>% mutate(sex = 'M')
MU018675.1 <- rbind(fem_MU018675.1,male_MU018675.1) %>% mutate(location = 'W chromosome')
MU018675.1

fem_MU017919.1 <- OJ_female %>% filter(chromosome == 'MU017919.1') %>% select(chromosome,coverage) %>% mutate(sex = 'F')
male_MU017919.1 <- OJ_male %>% filter(chromosome == 'MU017919.1') %>% select(chromosome,coverage) %>% mutate(sex = 'M')
MU017919.1 <- rbind(fem_MU017919.1,male_MU017919.1) %>% mutate(location = 'W chromosome')
MU017919.1

#MU018450.1	MU018386.1 MU017945.1	MU018675.1 MU017919.1			
```
```{r}
fem_MU018677.1 <- OJ_female %>% filter(chromosome == 'MU018677.1') %>% select(chromosome,coverage) %>% mutate(sex = 'F')
male_MU018677.1 <- OJ_male %>% filter(chromosome == 'MU018677.1') %>% select(chromosome,coverage) %>% mutate(sex = 'M')
MU018677.1 <- rbind(fem_MU018677.1,male_MU018677.1) %>% mutate(location = 'W chromosome')
MU018677.1

fem_MU018302.1 <- OJ_female %>% filter(chromosome == 'MU018302.1') %>% select(chromosome,coverage) %>% mutate(sex = 'F')
male_MU018302.1 <- OJ_male %>% filter(chromosome == 'MU018302.1') %>% select(chromosome,coverage) %>% mutate(sex = 'M')
MU018302.1 <- rbind(fem_MU018302.1,male_MU018302.1) %>% mutate(location = 'W chromosome')
MU018302.1

fem_MU018370.1 <- OJ_female %>% filter(chromosome == 'MU018370.1') %>% select(chromosome,coverage) %>% mutate(sex = 'F')
male_MU018370.1 <- OJ_male %>% filter(chromosome == 'MU018370.1') %>% select(chromosome,coverage) %>% mutate(sex = 'M')
MU018370.1 <- rbind(fem_MU018370.1,male_MU018370.1) %>% mutate(location = 'W chromosome')
MU018370.1

fem_MU018416.1 <- OJ_female %>% filter(chromosome == 'MU018416.1') %>% select(chromosome,coverage) %>% mutate(sex = 'F')
male_MU018416.1 <- OJ_male %>% filter(chromosome == 'MU018416.1') %>% select(chromosome,coverage) %>% mutate(sex = 'M')
MU018416.1 <- rbind(fem_MU018416.1,male_MU018416.1) %>% mutate(location = 'W chromosome')
MU018416.1

fem_MU017967.1 <- OJ_female %>% filter(chromosome == 'MU017967.1') %>% select(chromosome,coverage) %>% mutate(sex = 'F')
male_MU017967.1 <- OJ_male %>% filter(chromosome == 'MU017967.1') %>% select(chromosome,coverage) %>% mutate(sex = 'M')
MU017967.1 <- rbind(fem_MU017967.1,male_MU017967.1) %>% mutate(location = 'W chromosome')
MU017967.1

#MU017967.1	MU018416.1 MU018370.1 MU018302.1 MU018677.1
```
```{r}
fem_MU017909.1 <- OJ_female %>% filter(chromosome == 'MU017909.1') %>% select(chromosome,coverage) %>% mutate(sex = 'F')
male_MU017909.1 <- OJ_male %>% filter(chromosome == 'MU017909.1') %>% select(chromosome,coverage) %>% mutate(sex = 'M')
MU017909.1 <- rbind(fem_MU017909.1,male_MU017909.1) %>% mutate(location = 'W chromosome')
MU017909.1

fem_MU018361.1 <- OJ_female %>% filter(chromosome == 'MU018361.1') %>% select(chromosome,coverage) %>% mutate(sex = 'F')
male_MU018361.1 <- OJ_male %>% filter(chromosome == 'MU018361.1') %>% select(chromosome,coverage) %>% mutate(sex = 'M')
MU018361.1 <- rbind(fem_MU018361.1,male_MU018361.1) %>% mutate(location = 'W chromosome')
MU018361.1

fem_MU017883.1 <- OJ_female %>% filter(chromosome == 'MU017883.1') %>% select(chromosome,coverage) %>% mutate(sex = 'F')
male_MU017883.1 <- OJ_male %>% filter(chromosome == 'MU017883.1') %>% select(chromosome,coverage) %>% mutate(sex = 'M')
MU017883.1 <- rbind(fem_MU017883.1,male_MU017883.1) %>% mutate(location = 'W chromosome')
MU017883.1

fem_MU018405.1 <- OJ_female %>% filter(chromosome == 'MU018405.1') %>% select(chromosome,coverage) %>% mutate(sex = 'F')
male_MU018405.1 <- OJ_male %>% filter(chromosome == 'MU018405.1') %>% select(chromosome,coverage) %>% mutate(sex = 'M')
MU018405.1 <- rbind(fem_MU018405.1,male_MU018405.1) %>% mutate(location = 'W chromosome')
MU018405.1
#MU017909.1 MU018361.1 MU017883.1 MU018405.1
```

#combine all possible scaffold identities
```{r}
oxyJam.chromosome.locations <- rbind(CM021822.1, CM021821.1, CM021825.1, MU018450.1,	MU018386.1, MU017945.1,	MU018675.1, MU017919.1, MU017967.1,	MU018416.1, MU018370.1, MU018302.1, MU018677.1)
oxyJam.chromosome.locations
```
#plot male autosomes vs female autosomes
```{r}
autosome.M <- autosome.male.lst %>% rename(scaffold = X1, pos = X2, cov = X3) %>%  mutate(sex = 'M') %>% select(sex, cov)
autosome.M
autosome.F <- autosome.female.lst %>% rename(scaffold = X1, pos = X2, cov = X3) %>%  mutate(sex = 'F') %>% select(sex, cov)
autosome.merge <- rbind(autosome.F,autosome.M) %>% filter(cov < 100)
ggplot(autosome.merge, aes(cov, color = sex,y = ..density..)) + geom_freqpoly(alpha = 0.5, position = 'identity', binwidth = 3)
ggplot(autosome.merge, aes(cov, fill = sex)) + geom_histogram(alpha = 0.5, position = 'identity', binwidth = 3)
```
#plot male and female sex chromosomes
```{r}
fem_sexChr_plot <- fem_sexChr %>% mutate(sex = 'F')
male_sexChr_plot <- male_sexChr %>% mutate(sex = 'M')
sexChr.merge <- rbind(fem_sexChr_plot,male_sexChr_plot) %>% filter(cov < 100)
ggplot(sexChr.merge, aes(cov, color = sex,y = ..density..)) + geom_freqpoly(alpha = 0.5, position = 'identity', binwidth = 3)
ggplot(sexChr.merge, aes(cov, fill = sex)) + geom_histogram(alpha = 0.5, position = 'identity', binwidth = 3)
```
#calculate mean and median
```{r}
mean(autosome.M$cov) 
median(autosome.M$cov)
mean(autosome.F$cov)
median(autosome.F$cov)
mean(fem_sexChr$cov)
median(fem_sexChr$cov)
mean(male_sexChr$cov)
median(male_sexChr$cov)
```
#Make various plots
```{r}
ggplot(OJ_male, aes(x=coverage, y=log10(meandepth))) + geom_point()
ggplot(OJ_male, aes(x=coverage, y=meanmapq)) + geom_point()
ggplot(OJ_male, aes(x=meanmapq, y=log10(meandepth))) + geom_point()
ggplot(OJ_male, aes(x=coverage, y=log10(endpos))) + geom_point()
ggplot(OJ_male, aes(x=meanmapq, y=log10(endpos))) + geom_point()
```
```{r}
ggplot(OJ_female, aes(x=coverage, y=log10(meandepth))) + geom_point()
ggplot(OJ_female, aes(x=coverage, y=meanmapq)) + geom_point()
ggplot(OJ_female, aes(x=meanmapq, y=log10(meandepth))) + geom_point()
ggplot(OJ_female, aes(x=coverage, y=log10(endpos))) + geom_point()
ggplot(OJ_female, aes(x=meanmapq, y=log10(endpos))) + geom_point()
```
#normalize meandepth
```{r}
OJ_male %>% filter(endpos > 1e6) %>% mutate(weighted_depth = meandepth * endpos) %>% summarize(wt_norm_dp = sum(weighted_depth)/sum(endpos))
OJ_male_norm <- OJ_male %>% mutate(normdp = meandepth/37.05507)
OJ_male_norm
OJ_female %>% filter(endpos > 1e6, meandepth > 30) %>% mutate(weighted_depth = meandepth * endpos) %>% summarize(wt_norm_dp = sum(weighted_depth)/sum(endpos))
OJ_female_norm <- OJ_female %>% mutate(normdp = meandepth/40.69054)
OJ_female_norm
```
#plot normdp vs meanmapq and endpos to determine good cutoffs
```{r}
ggplot(OJ_female_norm, aes(x=meanmapq, y=log10(normdp))) + geom_point()
ggplot(OJ_female_norm, aes(x=log10(normdp), y=log10(endpos))) + geom_point()
ggplot(OJ_male_norm, aes(x=meanmapq, y=log10(normdp))) + geom_point()
ggplot(OJ_male_norm, aes(x=log10(normdp), y=log10(endpos))) + geom_point()
```
#plot normdp in males vs females
```{r}
OJ_both <- full_join(OJ_male_norm, OJ_female_norm, by=c('chromosome' = 'chromosome', 'endpos' = 'endpos'), suffix=c('.male', '.female')) 
OJ_both
OJ_both %>% filter(endpos > 1e5, meanmapq.female > 20, coverage.female > 50) %>% ggplot(aes(x=normdp.male, y=normdp.female)) + geom_point()
OJ_both %>% mutate(rel.dp = normdp.male / normdp.female) %>% filter(rel.dp < 3) %>% ggplot(aes(x=rel.dp)) + geom_histogram(bins = 60)
# filter(endpos > 1e4, meanmapq.female > 20, coverage.female > 50) %>%
``` 
W male 0-.15 fem 0.4-1.1
Z male 0.8-1 fem 0-1
autosome- male 0.8-1.2 fem 1.4-2.5

```{r}
OJ_W <- OJ_both %>% filter(normdp.female > 0.4,normdp.female < 1.1,normdp.male > 0, normdp.male < 0.15) %>% mutate(chr = 'W')
OJ_W
OJ_Z <- OJ_both %>% filter(normdp.female > 0,normdp.female < 1,normdp.male > 0.8, normdp.male < 1) %>% mutate(chr = 'Z')
OJ_Z
OJ_Auto <- OJ_both %>% filter(normdp.female > 1.4,normdp.female < 2.5,normdp.male > 0.6, normdp.male < 1.2) %>% mutate(chr = 'Autosome')
OJ_Auto
OJ_both_filtered <- rbind(OJ_Z,OJ_W,OJ_Auto) %>% mutate(rel.dp = normdp.male / normdp.female)
OJ_both_filtered
```

#add chromsome assignments to OJ_both
```{r}
ggplot(OJ_both_filtered, aes(x=rel.dp, col=chr))+ geom_histogram(bins=50)
ggplot(OJ_both_filtered, aes(x=rel.dp,y=normdp.female, col=chr))+ geom_point()
ggplot(OJ_both_filtered, aes(x=normdp.male,y=normdp.female, col=chr))+ geom_point()
```
#challenge our results
```{r}
OJ_both_filtered %>% filter(chr == 'W') %>% ggplot(aes(x=coverage.female, y=coverage.male))+ geom_point() #expect 100 coverage in fem, and expect lower coverage in males
```
#export list of w chromosomes to blast against chicken genome
```{r}
OJ_W.scaffolds <- OJ_both_filtered %>% select(chromosome,startpos.female, endpos,chr) %>% filter(chr == 'W') %>% unite(col = a, chromosome, startpos.female, sep = ';', remove = T) %>% unite(col = b, a, endpos, sep = '-', remove = T) %>% rename(position = b) %>% select(-chr)
OJ_W.scaffolds
write_tsv(OJ_W.scaffolds,'OJ_W.scaffolds.txt',col_names = F)
```

